The effects of priming in human computation

### 2014-05-08 docs/draft/pnas1.tex
finish prior work relating to amt quality studies

Variability raises a quality control issue. There have been many studies 
into how user interface design, payments, social reputation schemes, and the 
disclosure of the wider purpose of tasks affect worker outputs. We will 
review the prior work in the section following this one.
{\em Here, we report our investigation of worker {\em hysteresis}, that is, 
the tendency of a worker's output during one task to be influenced by other 
recently completed tasks}.

@@

\subsection*{Prior Work}
- human computation pioneered by von Ahn and L Dabbish when they demonstrated
	that images could be labeled by people via a game platform
	\cite{von2004labeling}

- Human computation is generally thought of in the context of crowdsourcing,
	which implies soliciting work in the form of an open call to an 
	unstructured pool of workers, general without any longterm engagement and 
	limited ability to screen workers screening of workers. 
	\cite{howe2008crowdsourcing}

- As such, quality assurance has received a lot of attention.
	- varying levels of attention and success \cite{kazai2013analysis}
	- Widely varying reports on accuracy from very negative 
	\cite{marsden2009crowdsourcing}, to positive 
	\cite{alonso2009can, grady2010crowdsourcing}
	- quality control \cite{lease2011quality}
		o filtering 
			- honeypots	\cite{snow2008cheap}
		o averaging
		- \cite{alonso2009can}, \cite{paolacci2010running}

	- training \cite{le2010ensuring}

	- prescreening, even for cultural effects
		\cite{paolacci2010running}
			- worker rep

	- game theoretic treatments
	- worker qualification 					  |	
	- price									  | \cite{kazai2013analysis}
	- task complexity						  |
	- spam, variability, adversarial behavior |

- effects of motivation
	for fun does badly, for money does well
	claimed expertize does badly
	interest does better than boring, and boring performs faster, 
	difficult does worse
	pay 'ok' does best

- studied effects of autonomy, skill use, and meaningfullness, in 
- other studies study the effects of reputation and social standing
- studied effect of giving workflow context\cite{Kinnaird2012281}
- studied effects of task design (user interface): \cite{Finnerty2013}

>>>>

Variability raises a quality control issue \cite{kazai2013analysis}. There 
have been many studies 
into how user interface design, payments, social reputation schemes, and the 
disclosure of the wider purpose of tasks affect worker outputs. We will 
review the prior work in the section following this one.
{\em Here, we report our investigation of worker {\em hysteresis}, that is, 
the tendency of a worker's output during one task to be influenced by other 
recently completed tasks}.

@@

\subsection*{Prior Work}

The notion of human computation in its modern form is attributed to von Ahn 
and L Dabbish for their demonstration of the \textit{ESP Game}, a system 
through which people label images by trying to guess the labels given by 
others \cite{von2004labeling}.  In this form, and on platforms like AMT,
is a kind of Crowdsourcing.

In crowdsourcing, an open call to is made an unstructured pool of workers 
\cite{howe2008crowdsourcing}.  There is generally no long-term engagement 
between worker and employer, and the ability 
to screen workers (say, for expertise) is usually very limited 
\cite{howe2008crowdsourcing}.  This raises its own quality issue 
\cite{lease2011quality}, distinct from the effects of hysteresis.

Reports on the reliability of crowdsourced output using AMT vary from very
bad \cite{marsden2009crowdsourcing} to quite good 
\cite{alonso2009can, grady2010crowdsourcing}. Kazai et al find that 
crowdsourced workers vary
greatly in their levels of attentiveness and accuracy, and that this 
variability in part depends on how interesting they find the task, whether they
judge
themselves to have expertise in the task domain, and whether they feel they
are being paid enough \cite{kazai2013analysis}.  Interestingly, workers that
indicated having expertise in the task were less likely to find it interesting,
spent less time on the task, and did more poorly.

Generally, some portion of responses appear to be random probably because
the worker is not bothering to actually perform the work as intended
\cite{lease2011quality}(check).  By including honeypots (traps that workers who are
catch workers who are not paying attention) such cheating can be screened out 
to some degree \cite{snow2008cheap}, as can filtering out repsonses
that have a very short completion time \cite{kazai2013analysis}.

The above methods could be considered post-processing, but pre-screening 
workers can be done as well. AMT provides the requester the ability to screen
workers based on their history of accepted task completions. But Paolacci et al
report good success in screening workers other attributes, even cultural ones
\cite{paolacci2010running}.  Training workers is another straightforward way 
to improve overall worker profficiency \cite{le2010ensuring}.

Other researchers have investigated how motivation, context, framing, and 
social factors affect worker performance.  Kazai et al found that workers 
motivated by payment were more accurate \cite{kazai2013analysis}, especially
if payment was neither too high nor too low.
A carefully designed user interface also improves worker performance 
\cite{Finnerty2013} as does telling the worker the wider workflow context that
of which their task is a part \cite{Kinnaird2012281}. Chandler and Kapelner
studied the effect of telling workers that their results would be used for
medical research, and found that workers were more likely to participate, but
did not provide more accurate work than when told nothing 
\cite{chandler2013breaking}.

Despite the wealth of research investigating the factors influencing 
performance in crowdsourcing, we are unable to find any work showing the 
effects of in-task priming as we have described it.  This is concerning 
because, in the psychology literature, it is well known that priming can have 
powerful effects especially for perceptual tasks related to recognizing 
words, gender, and affect---precisely the types of tasks for which AMT is used
\cite{yuen2011survey, snow2008cheap}.
